A general and efficient representation of Ancestral Recombination Graphs

### 2022-08-10 paper.tex
Move method survey to appendix

\subsection*{Differences in reconstructed ARGs}

There are a vast number of ARGs compatible with a given dataset, so ARG
reconstruction tools generally produce different outputs for the same input.
Figure \ref{fig-inferred-args} shows examples of the ARG topologies produced by
four of the tools mentioned above, applied to the classical dataset of 11
\emph{Drosophila melanogaster} sequences of \citet{kreitman1983nucleotide}.

>>>>

\section*{Differences in reconstructed ARGs}
ARGs inferred by different methods vary greatly in their properties.
To illustrate this, we examine the inferences made by four
recent methods on the classical \citet{kreitman1983nucleotide}.
\emph{Drosophila melanogaster} dataset.
